---
title: "reproduce-fat-exosome-microrna"
author: "jonathan dreyfuss"
date: "`r Sys.time()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("gplots")
source("functions/thomou-config.r")
```

##Purpose
To reproduce qPCR analyses, including statements in text and output, from Thomou et al. article.

##Adipose Tissue is a Major Source of Circulating Exosomal miRNAs
```{r read-wtvsko, echo=FALSE}
#######################################################################################################################
##mouse WT vs KO
#######################################################################################################################
wtvsko.ct <- read.csv("Ct_tables/ADicerKO-6mo-Ct.csv", row.names=1)
wtvsko.lst <- analyze_thomou_qPCR(ct=wtvsko.ct, contrasts.v=c(WTvsKO="WT-KO"))
wtvsko.pheno <- wtvsko.lst$pheno; wtvsko.stats <- wtvsko.lst$toptab
wtvsko.ndct <- wtvsko.lst$ndct; wtvsko.ndct.filt <- wtvsko.lst$ndct.filt
```

qPCR profiling of the serum exosomes for 709 miRNAs revealed 653 detectable miRNAs (Ct<34; see Supplemental Methods). Compared to control, ADicerKO mice exhibited significant alterations in 422 circulating miRNAs. Of these, only 3 miRNAs were significantly increased, while 419 had significant decreases (Figures 1c-d, Extended Data Figure 1d and Supplemental Table 1) with 88% reduced by >4-fold, suggesting that adipose tissue is a major source of circulating exosomal miRNAs.
```{r}
x <- nrow(wtvsko.ndct); if (x==709) cat(":-)") else cat(x)
x <- nrow(wtvsko.ndct.filt); if (x==653) cat(":-)") else cat(x)

x <- sum(wtvsko.stats$WTvsKO.p<0.05)
if (x==422) cat(":-)") else cat(x)
x <- sum(wtvsko.stats$WTvsKO.p<0.05 & wtvsko.stats$WTvsKO.logFC<0)
if (x==3) cat(":-)") else cat(x)
x <- sum(wtvsko.stats$WTvsKO.p<0.05 & wtvsko.stats$WTvsKO.logFC>0)
if (x==419) cat(":-)") else cat(x)
x <- round(sum(wtvsko.stats$WTvsKO.p<0.05 & wtvsko.stats$WTvsKO.FC>4)/419, 2)
if (x==0.88) cat(":-)") else cat(x)
```

Heatmap Fig 1c  
```{r fig1c}
heatmap(t(wtvsko.ndct.filt), scale="column", col=greenred(50), Rowv=NA, Colv=NA)

wtvsko.ndct.filt.sc <- scale(x=t(wtvsko.ndct.filt))
write.csv(t(wtvsko.ndct.filt.sc), "heatmap_z-scores/WTvsKO_ndct_filt_z.csv")
```

PCA in S1d  
```{r s1d}
#pca in fig s1d
s1d <- multi.pca(wtvsko.ndct, wtvsko.pheno, color='grp', shape='grp', name=NA, all.size=3, rm.leg.title=TRUE)
```


Consistent with this, among these most reduced miRNAs (Supplemental Table 1), many have been previously identified as highly expressed in fat, including miR-221, miR-201, miR-222 and miR-16.
```{r st1}
mirs.tmp <- paste0("mmu-", c("miR-221", "miR-201", "miR-222", "miR-16"))
x <- wtvsko.stats[mirs.tmp,"WTvsKO.logFC"]>0 & wtvsko.stats[mirs.tmp,"WTvsKO.p"]<0.05
if (all(x)) cat(":-)") else cat(mirs.tmp[!x])

#write supp table 1
st.cols <- c("p", "FDR", "logFC", "FC")
write.csv(wtvsko.stats[,paste0("WTvsKO.", st.cols)], "Supplemental_tables/ST1_ADicerKO-6mo-stats.csv")
```


Indeed, in sample of 80 miRNAs there was a broad reduction in total serum miRNAs in ADicerKO serum when compared to total serum of WT mice (Extended Data Figure 2a)  
```{r s1e, echo=FALSE}
#######################################################################################################################
##serum (6 month)
#######################################################################################################################
serum.ct <- read.csv("Ct_tables/WTvsKOserum-exo-ct.csv", row.names = 1)
serum.lst <- analyze_thomou_qPCR(serum.ct, contrasts.v = c(KOvsWTinSer="SerKO-SerWT", KOvsWTinExo="ExoKO-ExoWT"))
serum.ndct <- serum.lst$ndct; serum.ndct.filt <- serum.lst$ndct.filt
serum.toptab <- serum.lst$toptab

x <- nrow(serum.ndct); if (x==80) cat(":-)") else cat(x)
x <- mean(serum.toptab$KOvsWTinSer.logFC)
if (x < -1) cat(":-)") else cat(x)

heatmap(t(serum.ndct.filt[,ncol(serum.ndct.filt):1]), scale="column", Rowv=NA, Colv=NA, col=greenred(50))
serum.ndct.filt <- scale(x=t(serum.ndct.filt))
write.csv(t(serum.ndct.filt), "heatmap_z-scores/serum_ndct_z.csv")
```

Thus, in brown preadipocytes isolated from Dicer-floxed animals and recombined by transduction with Ad-Cre, there was reductions in >90% of the 359 detectable miRNAs (of 380 miRNAs profiled) released as exosomal miRNAs in the culture supernatants when compared to control Ad-GFP transduced cells (Extended Data Figure 2b).
```{r s2b}
#######################################################################################################################
##BAT preads
#######################################################################################################################
bat.pread.ct <- read.csv("Ct_tables/bat-pread-Ct.csv", row.names = 1)
bat.pread.lst <- analyze_thomou_qPCR(bat.pread.ct, contrasts.v = c(GFPvsCRE="GFP-CRE"))
bat.pread.ndct.filt <- bat.pread.lst$ndct.filt
bat.pread.stats.filt <- bat.pread.lst$toptab.filt

x <- nrow(bat.pread.lst$ndct); if (x==380) cat(":-)") else cat(x)
x <- nrow(bat.pread.ndct.filt); if (x==359) cat(":-)") else cat(x)

x <- table(sign(bat.pread.stats.filt$GFPvsCRE.logFC))/nrow(bat.pread.stats.filt)
if (x["1"] > 0.9) cat(":-)") else cat(x)

heatmap(t(bat.pread.ndct.filt[,ncol(bat.pread.ndct.filt):1]), scale="column", Rowv=NA, Colv=NA, col=greenred(50))
bat.pread.ndct.filt <- scale(x=t(bat.pread.ndct.filt))
write.csv(t(bat.pread.ndct.filt), "heatmap_z-scores/bat_pread_ndct_z.csv")
```

4 week old mice  
```{r wk4}
#######################################################################################################################
##4 week old mice
#######################################################################################################################
wk4.ct <- read.csv("Ct_tables/ADicerKO-4wk-Ct.csv", row.names=1)
wk4.lst <- analyze_thomou_qPCR(wk4.ct, norm.nm = "Mouse U6 snRNA", contrasts.v = c(YDvsWT="YD-WT"))
wk4.ndct.filt <- wk4.lst$ndct.filt
wk4.tt <- wk4.lst$toptab
```

To further dissociate altered metabolism from lipodystrophy as a cause of reduced exosomal miRNAs, we compared serum miRNAs from 4-week-old control and AdicerKO mice, since at this age the metabolic phenotypes of ADicerKO mice have not yet appeared (Extended Data Figure 2c). Again, of the 380 miRNAs profiled, 373 miRNAs were detectable with 202 down-regulated in ADicerKO mice and only 23 miRNAs up-regulated when compared to littermate controls, indicating that reduction in circulating miRNAs reflects primarily the difference in miRNA processing rather than the effect of chronic lipodystrophy. 
```{r}
#to find out how many are significantly up or down regulated at p<0.05
#filtering was applied using Ct<34 atleast twice
x <- nrow(wk4.tt); if (x==380) cat(":-)") else cat(x)
x <- nrow(wk4.ndct.filt); if (x==373) cat(":-)") else cat(x)

x <- table(sign(wk4.tt$YDvsWT.logFC[wk4.tt$YDvsWT.p<0.05]))
if (x["-1"]==202 & x["1"]==23) cat(":-)") else cat(x)
```

Extended Data Figure 2c (wk4 serum)  
```{r s2c}
heatmap(t(wk4.ndct.filt[,ncol(wk4.ndct.filt):1]), scale="column", col=greenred(50), Rowv=NA, Colv=NA)

wk4.ndct.filt.sc <- scale(x=t(wk4.ndct.filt))
write.csv(t(wk4.ndct.filt.sc), "heatmap_z-scores/wk4_serum_ndct_filt_z.csv")
```

human  
```{r read-human, echo=FALSE, include=FALSE}
#######################################################################################################################
##human
#######################################################################################################################
human.ct <- read.csv("Ct_tables/human-Ct.csv", row.names=1)
colnames(human.ct) <- gsub("PT", "CGL", colnames(human.ct))
human.lst <- analyze_thomou_qPCR(human.ct, filt.thresh=NA, norm.nm="Human U6 snRNA", contrasts.v = c(CGLvsCon="CGL-control", HIVvsCon="HIV-control"))
human.ndct <- human.lst$ndct
human.pheno <- human.lst$pheno
human.stats <- human.lst$toptab
```

Genome-wide qPCR profiling of 572 miRNAs in exosomes from human sera revealed 119 significantly different between control and HIV lipodystrophy subjects and 213 significantly different between control and CGL subjects (Figures1e-f, Extended Data Figure 3c, Supplemental Tables 2 and 3).   
```{r}
x <- nrow(human.ndct); if (x==572) cat(":-)") else cat(x)
x <- sum(human.stats$HIVvsCon.p <= 0.05); if (x==119) cat(":-)") else cat(x)
x <- sum(human.stats$CGLvsCon.p <= 0.05); if (x==213) cat(":-)") else cat(x)
```

heatmap 1e  
```{r 1e, echo=FALSE}
heatmap(t(human.ndct[,ncol(human.ndct):1]), Rowv=NA, Colv=NA, scale="column", col=greenred(50))

human.ndct.sc <- scale(x=t(human.ndct))
write.csv(t(human.ndct.sc), "heatmap_z-scores/human_ndct_z.csv")
```

waterfall plots 1f  
```{r 1f}
HIVvsCon.lfc <- sort(human.stats$HIVvsCon.logFC[human.stats$HIVvsCon.p < 0.05], decreasing=TRUE)
barplot(HIVvsCon.lfc, main="HIV vs Control log2FC")
write.table(HIVvsCon.lfc, "waterfall_logFCs/HIVvsControl_log2FC_waterfall.txt", row.names=FALSE, col.names=FALSE)

CGLvsCon.lfc <- sort(human.stats$CGLvsCon.logFC[human.stats$CGLvsCon.p < 0.05], decreasing=TRUE)
barplot(CGLvsCon.lfc, main="CGL vs Control log2FC")
write.table(CGLvsCon.lfc, "waterfall_logFCs/CGLvsControl_log2FC_waterfall.txt", row.names=FALSE, col.names=FALSE)
```

PCA S3c  
```{r s3c}
pca <- multi.pca(human.ndct, human.pheno, color='grp', shape='grp', name=NA, all.size=3, rm.leg.title=TRUE)
```

write supp tables 2 & 3  
```{r st2-3}
st2 <- human.stats[,paste0("HIVvsCon.", st.cols)]
write.csv(st2[order(st2$HIVvsCon.p),], "Supplemental_tables/ST2_HIVvsCon-stats.csv")

st3 <- human.stats[,paste0("CGLvsCon.", st.cols)]
write.csv(st3[order(st3$CGLvsCon.p),], "Supplemental_tables/ST3_CGLvsCon-stats.csv")
```


Of these, only 5% (29 miRNAs) were upregulated in either HIV or CGL, while 217 (38%) were down-regulated in either CGL or HIV lipodystrophy, with 75 decreased in both groups (Figure 1g, Supplemental Table 4). Again, several of these miRNAs (miR-201, miR-222 and miR-16) have been previously implicated in regulation of adipose tissue.  
```{r st4}
#create venn table, where value is sign of lfc if p<0.05, else value is 0 indicating not significant (ns)
venn.tab <- sign(human.stats[,grep("\\.logFC", colnames(human.stats))])
ns.ind <- which(human.stats[,grep("\\.p", colnames(human.stats))] > 0.05, arr.ind=TRUE)
venn.tab[ns.ind] <- 0
colnames(venn.tab) <- gsub("\\.logFC", "", colnames(venn.tab))
#remove rows where mir never significant to subset venn
venn.ss <- venn.tab[rowSums(abs(venn.tab))>=1,]

x <- sum(rowSums(venn.ss>0)>=1); if (x==29) cat(":-)") else cat(x)
x <- sum(rowSums(venn.ss<0)>=1); if (x==217) cat(":-)") else cat(x)
x <- sum(rowSums(venn.ss<0)==2); if (x==75) cat(":-)") else cat(x)

#match to fig 1g
vc <- vennCounts(venn.ss>0) #up
if (all(vc[-1, 3]==c(5, 13, 11))) cat(":-)") else cat(vc)
vc <- vennCounts(venn.ss<0) #down
if (all(vc[-1, 3]==c(28, 114, 75))) cat(":-)") else cat(vc)

#create table for venn, which is sorted for excel
st4 <- venn.ss[order(-rowSums(abs(venn.ss)), -2*venn.ss[,1]-venn.ss[,2]),]
write.csv(st4, "Supplemental_tables/ST4_HumanVenn.csv")

# mirs.tmp <- paste0("hsa-", c("miR-201", "miR-222", "miR-16"))
```

Thirty of the miRNAs that were decreased in serum of both patient cohorts were also decreased in the serum of the ADicerKO mice (Supplemental Table 5).  
```{r homo}
#homology was tested by equality of the mir name apart from the "hsa" or "mmu" prefix
hsa.both.nms <- rownames(venn.ss)[rowSums(venn.ss==-1)==2]
mmu.nms <- rownames(wtvsko.stats)[wtvsko.stats$WTvsKO.p<0.05 & wtvsko.stats$WTvsKO.logFC>0]
int.nms <- intersect(mmu.nms, sub("hsa", "mmu", hsa.both.nms))
if (length(int.nms)==30) cat(":-)") else cat(length(int.nms))

st5 <- data.frame(HomologDownMirs=gsub("mmu-", "", int.nms))

write.csv(st5, "Supplemental_tables/ST5_HomologDownMirs.csv", row.names = FALSE)
```


##Adipose Tissue Transplantation Reconstitutes Circulating miRNAs in Lipodystrophic Mice
```{r read_mmu_depot, echo=FALSE}
#######################################################################################################################
##depot
#######################################################################################################################
##normalize with global mean, but use expression of Ct above u6 for venn
depot.ct1 <- read.csv("Ct_tables/FatDepotsRepeats_Ct1.csv", row.names=1)
#SQ is ING in mouse
colnames(depot.ct1) <- gsub("SQ", "ING", colnames(depot.ct1))
depot.contr.v <- c(BATvsEPI="BAT-EPI", BATvsING="BAT-ING", EPIvsING="EPI-ING")
depot.u6.lst1 <- analyze_thomou_qPCR(depot.ct1, norm.nm="Mouse U6 (for mir 2-381)", filt.thresh=34, contrasts.v=depot.contr.v)
depot.ct2 <- read.csv("Ct_tables/FatDepotsRepeats_Ct2.csv", row.names=1)
colnames(depot.ct2) <- gsub("SQ", "ING", colnames(depot.ct2))
depot.u6.lst2 <- analyze_thomou_qPCR(depot.ct2, norm.nm="Mouse U6 (for miR 382-710)", filt.thresh=34, contrasts.v=depot.contr.v)
depot.u6.ndct <- rbind(depot.u6.lst1$ndct, depot.u6.lst2$ndct)
depot.pheno <- depot.u6.lst1$pheno

mean.mat <- t(apply(depot.u6.ndct, 1, FUN=function(v){
  tapply(v, INDEX=depot.pheno$grp, FUN=mean)
}))
```

miRNA profiling of subcutaneous inguinal (Ing) WAT, intraabdominal epididymal (Epi) WAT, and interscapular BAT from the normal donor mice taken at the time of transplantation revealed distinct, depot-specific signatures consistent with previous studies (Figure 2b).  

Using mean normalization from [Mestdagh et al, 2009](https://genomebiology.biomedcentral.com/articles/10.1186/gb-2009-10-6-r64).  
```{r 2bl_meannorm}
depot.heat.lst1 <- analyze_thomou_qPCR(depot.ct1, norm.nm="globalmean", filt.thresh=34, contrasts.v=depot.contr.v)
depot.heat.lst2 <- analyze_thomou_qPCR(depot.ct2, norm.nm="globalmean", filt.thresh=34, contrasts.v=depot.contr.v)

depot.heat.ndct.filt <- rbind(depot.heat.lst1$ndct.filt, depot.heat.lst2$ndct.filt)
heatmap(t(depot.heat.ndct.filt[,ncol(depot.heat.ndct.filt):1]), col=greenred(50), scale="column", Rowv=NA, Colv=NA)
depot.heat.ndct.filt.sc <- scale(x=t(depot.heat.ndct.filt))
write.csv(t(depot.heat.ndct.filt.sc), "heatmap_z-scores/depot_heat_ndct_filt_z.csv")
```

Venn of mirs over u6 (fig 2b), independent of global avg.  
```{r 2br}
vennDiagram(vennCounts(mean.mat>0), circle.col = c("blue", "red", "yellow"))
```

Considering only the miRNAs that were expressed in at least one fat depot, 126 were highly expressed in BAT, 106 in Ing-WAT, and 160 in Epi-WAT, with 82 of these miRNAs expressed in all three depots (Figures 2b, Extended Data Figure 4a; Supplemental Table 6).
```{r}
if (all(colSums(mean.mat>0)==c(126, 160, 106) & colnames(mean.mat)==c("BAT", "EPI", "ING"))) cat(":-)") else colSums(mean.mat>0)

#use globalmean norm for stats
depot.tt <- rbind(depot.heat.lst1$toptab, depot.heat.lst2$toptab)
st6 <- depot.tt[,-grep("\\.avg", colnames(depot.tt))]
write.csv(st6, "Supplemental_tables/ST6_Depot-stats.csv")
```

with 82 of these miRNAs expressed in all three depots.
```{r}
x <- sum(rowSums(mean.mat>0)==3)
if (x==82) cat(":-)") else cat (x)
```  

PCA S4a  
```{r s4a}
depot.heat.ndct <- rbind(depot.heat.lst1$ndct, depot.heat.lst2$ndct)
# s2a <- multi.pca(depot.heat.ndct, depot.pheno, color='grp', shape='grp', name="mouse_depots_repeat/meannorm_pca", all.size=3, rm.leg.title=TRUE)
s2a <- multi.pca(depot.heat.ndct, depot.pheno, color='grp', shape='grp', name=NA, all.size=3, rm.leg.title=TRUE)
```  

##Transplant data
```{r read_transplant}
#######################################################################################################################
##transplant
#######################################################################################################################
trans.ct <- read.csv("Ct_tables/transplant-exo-Ct.csv", row.names=1)
colnames(trans.ct) <- gsub("SQ", "ING", colnames(trans.ct))
trans.grp <- gsub('[0-9]$', '', colnames(trans.ct))
#ron only wants to analyze those where mean(WT)<34 
wt.expr <- rowMeans(trans.ct[,trans.grp=="WT"]) < 34
trans.ct.ss <- trans.ct[wt.expr,]

trans.lst <- analyze_thomou_qPCR(trans.ct.ss, filt.thresh=NA, contrasts.v = c(SALvsWT="SAL-WT", BATvsSAL="BAT-SAL", EPIvsSAL="EPI-SAL", INGvsSAL="ING-SAL"))
trans.toptab <- trans.lst$toptab
trans.ndct <- trans.lst$ndct
trans.pheno <- trans.lst$pheno
#ron then wants to see which went down in SAL (p<0.05)
trans.toptab.ss <- trans.toptab[trans.toptab$SALvsWT.p < 0.05 & trans.toptab$SALvsWT.logFC < 0,]

#finally ron wants to see whose expr went up >50% of the way to WT (i'll do on log scale)
rescue.col.nms <- c("BAT", "EPI", "ING")
#use CT scale for comparing to halfway
trans.toptab.ss$half.avg <- (trans.toptab.ss$WT.avg+trans.toptab.ss$SAL.avg)/2
rescue.half <- apply(trans.toptab.ss[,paste0(rescue.col.nms, ".avg")], MARGIN=2, 
                    FUN=function(v){ v > trans.toptab.ss$half.avg })
#as with previous mouse analysis, also check that Ct of depot <34
ct.means <- t(apply(trans.ct, 1, FUN=function(v) tapply(v, trans.grp, mean, na.rm=TRUE)))
rescue.ct <- ct.means[rownames(trans.toptab.ss), rescue.col.nms] < 34

#also check that DepotvsSAL.p<0.05
p.tab <- trans.toptab.ss[,paste0(rescue.col.nms, "vsSAL.p")]
rescue.p <- p.tab < 0.05

#combine 3 matrices logically
rescue.mat <- rescue.p & rescue.ct & rescue.half
colnames(rescue.mat) <- rescue.col.nms
```

As in the first cohort, in the sham-operated ADicerKO mice circulating exosomal miRNAs were markedly reduced compared to controls (Figure 2c). By comparison, ADicerKO mice that received fat transplants showed remarkable restoration of circulating exosomal miRNAs (Figures 2c and Extended Data Figure 5a; Supplemental Tables 7 and 8). 
```{r 2c}
##trans.ndct has all mirs where mean(WT)<34
heatmap(t(trans.ndct[,ncol(trans.ndct):1]), col=greenred(50), scale="column", Rowv=NA, Colv=NA)
#write out for TT to submit as underlying data
trans.ndct.sc <- scale(x=t(trans.ndct))
write.csv(t(trans.ndct.sc), "heatmap_z-scores/trans_heat_ndct_z.csv")

# rescue.mat <- read.csv("mouse_transplants/transplant_rescue_matrix.csv", row.names=1)
vennDiagram(vennCounts(rescue.mat), circle.col = c("blue", "red", "yellow"))
vc <- vennCounts(rescue.mat)
rescue.trans.totals <- apply(vc[,1:3], MARGIN=2, FUN=function(v){ sum(vc[v==1, "Counts"]) })

st7 <- rescue.mat[rowSums(rescue.mat) > 0,] #only keep rows with a rescue
write.csv(st7, "Supplemental_tables/ST7_MouseDepotRescue.csv")

st8 <- trans.toptab.ss[,-grep("\\.avg", colnames(trans.toptab.ss))]
write.csv(st8, "Supplemental_tables/ST8_TransplantComparisons.csv")
```  

PCA S5a  
```{r s5a}
pca <- multi.pca(trans.ndct, trans.pheno, color='grp', shape='grp', name=NA, all.size=3, rm.leg.title=TRUE)
# pca <- multi.pca(trans.ndct, trans.pheno, color='grp', shape='grp', name="../mouse_transplants/transplant_pca", all.size=3, rm.leg.title=TRUE)
```  

Indeed, of the circulating exosomal miRNAs profiled, 375 revealed detectable levels of expression (Ct<34), and most of which were significantly decreased in ADicerKO serum, fat transplantation restored the levels of 150, 110, and 116 at least 50% of the way to normal in mice receiving BAT, Epi-WAT and Ing-WAT transplants, respectively.

Indeed, of the 177 circulating exosomal miRNAs that were detectable in wild-type and significantly decreased in ADicerKO serum, fat transplantation restored the levels of the majority of these at least 50% of the way to normal... 
```{r rescue}
mir.wt <- setdiff(rownames(trans.ct)[rowMeans(trans.ct[,trans.grp=="WT"])<34], "Mouse U6 snRNA")
x <- sum(trans.toptab[mir.wt, "SALvsWT.logFC"]<0 & trans.toptab[mir.wt, "SALvsWT.p"]<0.05)
if (x==177) cat(":-)") else cat(x)

x <- mean(colSums(rescue.mat)); if (x > 177/2) cat(":-)") else { cat(x) }
```

Four miRNA candidates were identified (miR-99a, miR-99b, miR-100, and miR-466i), and three of these (miR-99a, -99b, and -100) were significantly decreased in the serum of ADicerKO mice compared to controls.   
```{r fgf21a}
#######################################################################################################################
##fgf21
#######################################################################################################################
mirs.tmp <- paste0("mmu-", c("miR-99a", "miR-99b", "miR-100"))
x <- trans.toptab[mirs.tmp, "SALvsWT.p"] < 0.05 & trans.toptab[mirs.tmp, "SALvsWT.logFC"] < 0 & mirs.tmp %in% rownames(trans.toptab)
if (all(x)) cat(":-)") else cat(mirs.tmp[!x])
```

This was consistent with the fact that these three miRNAs were also highly expressed in both BAT and WAT
```{r fgf21b}
#this refers to depot expression, highly expressed=above u6
x <- mean.mat[mirs.tmp,]
if (all(x > -1)) cat(":-)") else cat(":-(")
```

and after BAT or WAT transplantation, there was a >=50% recovery of these miRNAs in the serum of ADicerKO mice (Extended Data Figure 6b).
```{r fgf21c}
x <- rescue.mat[intersect(mirs.tmp, rownames(rescue.mat)),]
if (all(x)) cat(":-)") else cat(":-(")
```

Extended Data Figure 6b  
```{r s6b}
mirs.s6b <- paste0("mmu-", c("miR-99a", "miR-99b", "miR-100", "miR-466i"))
stopifnot(all(mirs.s6b %in% rownames(trans.toptab)))
mirs.lfc <- trans.toptab[mirs.s6b, grep("\\.logFC", colnames(trans.toptab))]
colnames(mirs.lfc) <- gsub("\\.logFC", "", colnames(mirs.lfc))
#flip comparison of SALvsWT to WTvsSAL
mirs.lfc$SALvsWT <- -1*mirs.lfc$SALvsWT
colnames(mirs.lfc) <- gsub("SALvsWT", "WTvsSAL", colnames(mirs.lfc))
#line up plot with TT's in supp
barplot(as.matrix(t(mirs.lfc[,c(1,3,4,2)])), beside=TRUE, las=2, legend.text=TRUE, args.legend=list(x="top"))
```

##Session Info  
```{r session}
sessionInfo()
```

```{r check}
##check my code
all.equal(mean(trans.ndct["mmu-miR-22", trans.grp=="SAL"])-mean(trans.ndct["mmu-miR-22", trans.grp=="WT"]), trans.toptab["mmu-miR-22", "SALvsWT.logFC"])
"mmu-miR-449b" %in% mmu.nms & "hsa-miR-449b" %in% hsa.both.nms
```

